MSAD_PCA_Walkthrough

### 2017-07-13 LaTeX_Vignette/MS-MVSPC_DissertationVignette.Rnw
Edited section 5.3

\subsection{Why use \texttt{mvMonitoring}?}
The \texttt{mvMonitoring} package can be used to detect outliers in a correlated, non-Gaussian multivariate process with non-linear, non-stationary, or autocorrelated feature behavior. These process outliers are often indicative of system fault. The naive (and unfortunately common) approach to multivariate process monitoring is to use expert opinion to identify a few important features to monitor visually, and raise an alarm if these features travel outside pre-defined normal operating boundaries.

@@

\section{Simulating Data with \texttt{mspProcessData}} \label{sec:D_DataGen}
This function generates three-dimensional multi-state or single-state non-linear, non-stationary, and autocorrelated process observations. We follow the seminal work of \cite{dong_batch_1996} for generation of the foundational stationary and independent features.

\subsection{Latent Feature Creation}
So that the simulated features have non-zero correlations, Dong and McAvoy created their three features all as polynomial functions of a single latent variable $t(s)$, where $s = 1, \ldots, \omega$ is the observational index of the process.

\subsubsection{Autocorrelated and Non-Stationary Error}
The \texttt{mspProcesData} function induces autocorrelation in $t$ through its errors, $\varepsilon_s$, where
\[
  \varepsilon_1 \sim \mathcal{N}\left(\frac{1}{2}(a + b)(1 - \phi), \frac{b - a}{12} (1 - \phi ^ 2)\right),
\]
where $a = 0.01$ and $b = 2$. Now, we define the first-order autoregressive process on $\varepsilon_s$ by
\[
  \varepsilon_s = \varphi\varepsilon_{s - 1} + (1 - \varphi)\varepsilon,
\]
where $\varepsilon$ is as defined in the previous expression and the autocorrelation component $\phi = 0.75$. The mean and variance multipliers are the mean and variance of a random variable from the $\mathcal{U}_{[a,b]}$ distribution.

\subsubsection{The Non-Linear Latent Process}
This $t$ vector will be sinusoidal with period $\omega = 7 * 24 * 60$ (signifying a weekly period in  minute-level observations). We then synthesize a $t$ with
\[
  t^*_s = -\cos\left( \frac{2\pi}{\omega} s \right) + \epsilon_s,
\]
and scale $t^*$ to
\[
  t = \frac{(b - a)(t^*_s - \text{min}(t^*_s))}{\text{max}(t^*_s) - \text{min}(t^*_s)} + a.
\]
Finally then, the $t$ vector will lie entirely in $[a,b]$.

@@

\subsubsection{Single State Features}
First \texttt{mspProcessData} simulates three features, with each feature operating under $k$ different states. Let $\langle x_k(t), y_k(t), z_k(t) \rangle$ be the notation for State $k$. These are the three features under State 1 (normal operating conditions, or \emph{NOC}) as three functions of $t$:
\begin{align}
\textbf{x}(\textbf{t}) &\equiv \textbf{t} + \boldsymbol\varepsilon_1, \\
\textbf{y}(\textbf{t}) &\equiv \textbf{t} ^ 2 - 3 * \textbf{t} + \boldsymbol\varepsilon_2, \\
\textbf{z}(\textbf{t}) &\equiv -\textbf{t} ^ 3 + 3 * \textbf{t} ^ 2 + \boldsymbol\varepsilon_3,
\end{align}
where $\varepsilon_i \sim N(0, 0.01)$. The \texttt{mspProcessData} function calls the internal \texttt{processNOCdata} function to generate single-state observations under NOC.

\subsubsection{Multi-State Features}
The multi-state feature expression is induced by rotation and scaling of certain sets of observations. To induce a three-state, hourly switching process (the default), the \texttt{mspProcessData} function will create a label column that switches from ``1'' to ``2'' to ``3'' every hour. State ``1'' will be the features generated under the single-state assumption, while State ``2'' and State ``3'' are generated as follows. These states will be scaled rotations of the current $\langle x,y,z \rangle$ set. The second state is yaw, pitch, and roll rotated by (0, 90, 30) degrees, and the scales are multiplied by (1, 0.5, 2). The third state is yaw, pitch, and roll rotated by (90, 0, -30) degrees, and the scales are multiplied by (0.25, 0.1, 0.75).
\begin{enumerate}
\item $\mathcal{S}_1$: $\textbf{X}(t_s) := \langle x(t_s), y(t_s), z(t_s)\rangle$.

@@

\subsection{Synthetic Fault Induction}
Faults can be introduced to single- or multi-state data via the \texttt{mspProcessData} function. The default fault start index is 8500, or roughly 84\% through the 10,080 observation cycle. These faults are added through the internal \texttt{faultSwitch} function.
\begin{enumerate}
\item Fault 1A is a positive shift to all three features before state rotation: $\textbf{X}^*(t_s) = \textbf{X}(t_s) + 2,\ s \ge 8500$.
%
\item Fault 1B is a positive shift to the $x$ feature before state rotation: $x^*(t_s) = x(t_s) + 2,\ s \ge 8500$.
%
\item Fault 1C is a positive shift to the $x$ and $z$ features in State 3 only and *after* state rotation: $x^*(t_s) = x(t_s) + 2,\ z^*(t_s) = z(t_s) + 2,\ s \ge 8500$.
%
\item Fault 2A is a positive drift across all the process monitoring features before state rotation: $\textbf{X}^*(t_s) = \textbf{X}(t_s) + (s - 8500)\times 10^{-3}$, $s > 8500$.
%
\item Fault 2B is a positive drift across the $y$ and $z$ process monitoring features before state rotation: $y^*(t_s) = y(t_s) + (s - 8500)\times 10^{-3},\ z^*(t_s) = z(t_s) + (s - 8500)\times 10^{-3}$, $s > 8500$.
%
\item Fault 2C is a negative drift in the $y$ process monitoring feature in State 2 only and \emph{after} state rotation: $y^*(t_s) = y(t_s) - 1.5 \times \frac{s - 8500}{10080 - 8500}$, for $s > 8500$.
%
\item Fault 3A is an amplification of the underlying latent variable $t$ for all features. The maximum latent drift of this fault will be 5 + 1: $\textbf{X}^*(t_s) = \textbf{X}(t_s^*),\ s > 8500$, where $t_s^* = \left[\frac{5(s - 8500)}{\omega - 8500} + 1\right]t_s$.
%
\item Fault 3B is a mutation of the underlying latent variable $t$ for the $z$ feature: $z^*(t_s) = z(\log t_s^*)$, $s \ge 8500$. This fault will dampen the underlying latent effect for $z$ if $t_s > 1$ and amplify this effect if $t_s < 1$.
%
\item Fault 3C is a polynomial mutation of the error for the $y$ feature in State 2 only and \emph{after} state rotation: $y^*(t_s) = y(t_s) + 2 * \textbf{e}_3(s) - 0.25$, for $s > 8500$.
\end{enumerate}

\subsection{Putting it all together\ldots}
The \texttt{mspProcessData} function can generate weeks' worth of non-linear, non-stationary, autocorrelated, multi-state, multivariate process data useful to test new process monitoring techniques. Users can generate observations under NOC to measure false alarm rates, or induce one of nine pre-built faults to test detection time and consistency with repeated Monte Carlo sampling. We expect this function will generate interesting data useful enough to compare new and improved process monitoring techniques with existing methods.

>>>>

\subsection{Why use \texttt{mvMonitoring}?}
The \texttt{mvMonitoring} package can be used to detect outliers in a correlated, non-Gaussian multivariate process with non-linear, non-stationary, or autocorrelated feature behavior. These process outliers are often indicative of system fault. The naive (but unfortunately common) approach to multivariate process monitoring is to use expert opinion to identify a few important features to monitor visually, and raise an alarm if these features travel outside pre-defined normal operating boundaries.

@@

\section{Simulating Data with \texttt{mspProcessData}} \label{sec:D_DataGen}
The \texttt{mspProcessData} function generates three-dimensional multi-state or single-state non-linear, non-stationary, and autocorrelated process observations. We follow the seminal work of \cite{dong_batch_1996} for generation of the foundational stationary and independent features.

\subsection{Latent Feature Creation}
So that the simulated features have non-zero correlations, Dong and McAvoy created their three features all as polynomial functions of a single latent variable $t_s$, where $s = 1, \ldots, \omega$ is the observational index of the process.

\subsubsection{Autocorrelated and Non-Stationary Error}
The \texttt{mspProcesData} function induces autocorrelation in $t$ through its errors, $\varepsilon_s$, where
\[
  \varepsilon_1 \sim \mathcal{N}\left(\frac{1}{2}(a + b)(1 - \varphi), \frac{b - a}{12} (1 - \varphi ^ 2)\right),
\]
where $a = 0.01$ and $b = 2$. Now, we define the first-order autoregressive process on $\varepsilon_s$ by
\[
  \varepsilon_s = \varphi\varepsilon_{s - 1} + (1 - \varphi)\varepsilon,
\]
where $\varepsilon$ is a random innovation drawn from the Normal distribution defined in the previous expression, and the autocorrelation component $\varphi = 0.75$. The mean and variance multipliers are the mean and variance of a random variable from the $\text{uniform}_{[a,b]}$ distribution.

\subsubsection{The Non-Linear Latent Process}
This $t$ vector will be sinusoidal with period $\omega = 7 * 24 * 60$ (signifying a weekly period in  minute-level observations). We then synthesize a $t$ by taking
\[
  t^*_s = -\cos\left( \frac{2\pi}{\omega} s \right) + \epsilon_s,
\]
and then scaling $t^*$ to
\[
  t = \frac{(b - a)(t^*_s - \text{min}(t^*_s))}{\text{max}(t^*_s) - \text{min}(t^*_s)} + a.
\]
Finally then, the $t$ vector will lie entirely in $[a,b]$.

@@

\subsubsection{Single State Features}
First \texttt{mspProcessData} simulates three features, with each feature operating under $k$ different states. Let $\langle x_k(t_s), y_k(t_s), z_k(t_s) \rangle$ be the process evaluated at $t_s$ within State $k$. These are the three features under State 1 (in control, or \emph{IC}) as three functions of $t$:
\begin{align}
x(\textbf{t}) &\equiv \textbf{t} + \boldsymbol\varepsilon_1, \\
y(\textbf{t}) &\equiv \textbf{t} ^ 2 - 3 * \textbf{t} + \boldsymbol\varepsilon_2, \\
z(\textbf{t}) &\equiv -\textbf{t} ^ 3 + 3 * \textbf{t} ^ 2 + \boldsymbol\varepsilon_3,
\end{align}
where $\varepsilon_i \sim N(0, 0.01),\ 1 = 1, 2, 3$. The \texttt{mspProcessData} function calls the internal \texttt{processNOCdata} function to generate IC single-state observations.

\subsubsection{Multi-State Features}
The multi-state feature expression is induced by rotation and scaling of certain sets of observations. To induce a three-state, hourly switching process (the default), the \texttt{mspProcessData} function will create a label column that switches from ``1'' to ``2'' to ``3'' every hour. State ``1'' will be the features generated under the single-state assumption, while State ``2'' and State ``3'' are generated as follows. These states will be scaled rotations of the current $\langle x,y,z \rangle$ set. The second state is yaw, pitch, and roll rotated by (0, 90, 30) degrees, and the scales are multiplied by (1, 0.5, 2). The third state is yaw, pitch, and roll rotated by (90, 0, -30) degrees, and the scales are multiplied by (0.25, 0.1, 0.75). That is,
\begin{enumerate}
\item $\mathcal{S}_1$: $\textbf{X}(t_s) := \langle x(t_s), y(t_s), z(t_s)\rangle$.

@@

\subsection{Synthetic Fault Induction}
Faults can be introduced to single- or multi-state data via the \texttt{mspProcessData} function. The default fault start index is 8500, or roughly 84\% through the cycle of 10,080 observations. These faults are added through the internal \texttt{faultSwitch} function.
\begin{enumerate}
\item Fault 1A is a positive shift to all three features before state rotation: $\textbf{X}^*(t_s) = \textbf{X}(t_s) + 2,\ s \ge 8500$.
%
\item Fault 1B is a positive shift to the $x$ feature before state rotation: $x^*(t_s) = x(t_s) + 2,\ s \ge 8500$.
%
\item Fault 1C is a positive shift to the $x$ and $z$ features in State 3 only and \emph{after} state rotation: $x^*(t_s) = x(t_s) + 2,\ z^*(t_s) = z(t_s) + 2,\ s \ge 8500$.
%
\item Fault 2A is a positive drift across all the process monitoring features before state rotation: $\textbf{X}^*(t_s) = \textbf{X}(t_s) + (s - 8500)\times 10^{-3}$, $s > 8500$.
%
\item Fault 2B is a positive drift across the $y$ and $z$ process monitoring features before state rotation: $y^*(t_s) = y(t_s) + (s - 8500)\times 10^{-3},\ z^*(t_s) = z(t_s) + (s - 8500)\times 10^{-3}$, $s > 8500$.
%
\item Fault 2C is a negative drift in the $y$ process monitoring feature in State 2 only and \emph{after} state rotation: $y^*(t_s) = y(t_s) - 1.5 \times \frac{s - 8500}{10080 - 8500}$, for $s > 8500$.
%
\item Fault 3A is an amplification of the underlying latent variable $t$ for all features. The maximum latent drift of this fault will be 5 + 1: $\textbf{X}^*(t_s) = \textbf{X}(t_s^*),\ s > 8500$, where $t_s^* = \left[\frac{5(s - 8500)}{\omega - 8500} + 1\right]t_s$.
%
\item Fault 3B is a mutation of the underlying latent variable $t$ for the $z$ feature: $z^*(t_s) = z(\log t_s^*)$, $s \ge 8500$. This fault will dampen the underlying latent effect for $z$ if $t_s > 1$ and amplify this effect if $t_s < 1$.
%
\item Fault 3C is a polynomial mutation of the error for the $y$ feature in State 2 only and \emph{after} state rotation: $y^*(t_s) = y(t_s) + 2 * \textbf{e}_3(s) - 0.25$, for $s > 8500$.
\end{enumerate}

\subsection{Putting it all together\ldots}
The \texttt{mspProcessData} function can generate weeks' worth of non-linear, non-stationary, autocorrelated, multi-state, multivariate process data useful to test new process monitoring techniques. Users can generate IC observations to measure false alarm rates, or induce one of nine pre-built faults to test detection time and consistency with repeated Monte Carlo sampling. We expect this function will generate interesting data useful enough to compare new and improved process monitoring techniques with existing methods. A detailed description of this function's inputs and outputs are shown in Section \ref{sec:D_Workflow}.

### 2017-07-13 LaTeX_Vignette/MS-MVSPC_DissertationVignette.tex
Edited section 5.3

##   Data: num [1:4142, 1:5] 2.084 0.268 0.582 0.694 0.956 ...

@@

##   .. ..$ SPE_threshold   : Named num 4.66

@@

##   .. ..$ T2_threshold    : Named num 58.1

@@

##   .. ..$ projectionMatrix: num [1:6, 1:2] 0.421 -0.386 0.434 0.429 -0.325 ...
##   .. ..$ LambdaInv       : num [1:2, 1:2] 0.202 0 0 1.685
##   .. ..$ muTrain         : Named num [1:6] 1.38 -2.08 2.95 1.36 -2.04 ...

@@

##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 2.47 0 0 0 0 ...

@@

##   .. ..$ SPE_threshold   : Named num 1.06

@@

##   .. ..$ T2_threshold    : Named num 77.4

@@

##   .. ..$ projectionMatrix: num [1:6, 1:3] -0.50267 -0.00244 0.49616 -0.52609 -0.14826 ...
##   .. ..$ LambdaInv       : num [1:3, 1:3] 0.285 0 0 0 0.706 ...
##   .. ..$ muTrain         : Named num [1:6] 2.958 -0.564 -4.481 2.931 -0.59 ...

@@

##   .. ..$ SPE_threshold   : Named num 6.33

@@

##   .. ..$ T2_threshold    : Named num 80.1

@@

##   .. ..$ projectionMatrix: num [1:6, 1:2] -0.403 -0.456 -0.459 0.135 -0.458 ...
##   .. ..$ LambdaInv       : num [1:2, 1:2] 0.273 0 0 0.505
##   .. ..$ muTrain         : Named num [1:6] 0.523 0.269 1.409 0.565 0.255 ...

@@

##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 15.4 0 0 0 0 ...

@@

\subsubsection{Adding Lagged Features}
First, concatenate the last given observation from the training set as ``row 0'' of the test data set. This will enable \texttt{mspMonitor} to include lag-1 features. Similarly, one would include the last $k$ observations of the training set should the process dictate the need for any lag-$k$ features. Because the Fault Start Index was set to 8500, this testing window will show the change point between observations generated under normal conditions and those generated under a fault state.
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{test1A_xts} \hlkwb{<-} \hlstd{fault1A_xts[}\hlnum{8460}\hlopt{:}\hlnum{8520}\hlstd{,} \hlopt{-}\hlnum{1}\hlstd{]}
\hlstd{lagTest1A_xts} \hlkwb{<-} \hlkwd{lag.xts}\hlstd{(test1A_xts,} \hlnum{0}\hlopt{:}\hlnum{1}\hlstd{)}
\hlstd{lagTest1A_xts} \hlkwb{<-} \hlkwd{cbind}\hlstd{(fault1A_xts[}\hlnum{8461}\hlopt{:}\hlnum{8520}\hlstd{,}\hlnum{1}\hlstd{],}
                       \hlstd{lagTest1A_xts[}\hlopt{-}\hlnum{1}\hlstd{,])}
\hlkwd{head}\hlstd{(lagTest1A_xts)}
\end{alltt}
\begin{verbatim}
##                     state         x         y         z       x.1
## 2015-05-22 07:00:00     1 0.6030535 -1.566528 0.8662376 0.3665282
## 2015-05-22 07:01:00     1 0.4416746 -1.406672 0.3811997 0.6030535
## 2015-05-22 07:02:00     1 0.5408433 -1.304789 0.4314055 0.4416746
## 2015-05-22 07:03:00     1 0.5082937 -1.391546 0.8054482 0.5408433
## 2015-05-22 07:04:00     1 0.4508361 -1.312723 0.8291703 0.5082937
## 2015-05-22 07:05:00     1 0.7068563 -1.465259 0.7728310 0.4508361
##                             y.1       z.1
## 2015-05-22 07:00:00  0.08751379 0.3336879
## 2015-05-22 07:01:00 -1.56652763 0.8662376
## 2015-05-22 07:02:00 -1.40667237 0.3811997
## 2015-05-22 07:03:00 -1.30478897 0.4314055
## 2015-05-22 07:04:00 -1.39154587 0.8054482
## 2015-05-22 07:05:00 -1.31272320 0.8291703
\end{verbatim}
\end{kframe}
\end{knitrout}

\subsubsection{Monitoring the Test Data}
With the lagged test observations in the working environment, the \texttt{mspMonitor} function can be applied. This function (similarly to \texttt{mspTrain}) takes in the label information as a separate argument from the input data. Further, the \texttt{mspMonitor} function takes in the \texttt{TrainingSpecs} object returned in the results list from \texttt{mspTrain}. Notice that the first six rows of the monitor matrix are the exact same as the first six rows of the lagged test matrix, except that the rows of the monitor matrix have the monitoring statistic and corresponding indicator columns appended.
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{monitor1A_xts} \hlkwb{<-} \hlkwd{mspMonitor}\hlstd{(}\hlkwc{observations} \hlstd{= lagTest1A_xts[,}\hlopt{-}\hlnum{1}\hlstd{],}
                            \hlkwc{labelVector} \hlstd{= lagTest1A_xts[,}\hlnum{1}\hlstd{],}
                            \hlkwc{trainingSummary} \hlstd{= train1A_ls}\hlopt{$}\hlstd{TrainingSpecs)}
\hlkwd{head}\hlstd{(monitor1A_xts)}
\end{alltt}
\begin{verbatim}
##                             x         y         z       x.1         y.1
## 2015-05-22 07:00:00 0.6030535 -1.566528 0.8662376 0.3665282  0.08751379
## 2015-05-22 07:01:00 0.4416746 -1.406672 0.3811997 0.6030535 -1.56652763
## 2015-05-22 07:02:00 0.5408433 -1.304789 0.4314055 0.4416746 -1.40667237
## 2015-05-22 07:03:00 0.5082937 -1.391546 0.8054482 0.5408433 -1.30478897
## 2015-05-22 07:04:00 0.4508361 -1.312723 0.8291703 0.5082937 -1.39154587
## 2015-05-22 07:05:00 0.7068563 -1.465259 0.7728310 0.4508361 -1.31272320
##                           z.1       SPE SPE_Flag        T2 T2_Flag Alarm
## 2015-05-22 07:00:00 0.3336879 0.7953977        0 24.566074       0    NA
## 2015-05-22 07:01:00 0.8662376 0.3442694        0  5.731867       0    NA
## 2015-05-22 07:02:00 0.3811997 0.4382832        0  6.232419       0    NA
## 2015-05-22 07:03:00 0.4314055 0.2334754        0  5.558003       0    NA
## 2015-05-22 07:04:00 0.8054482 0.5248950        0  5.476091       0    NA
## 2015-05-22 07:05:00 0.8291703 0.1880696        0  4.896475       0    NA
\end{verbatim}
\end{kframe}
\end{knitrout}

>>>>

##   Data: num [1:4142, 1:5] 0.2407 0.0621 0.2815 0.1616 0.3386 ...

@@

##   .. ..$ SPE_threshold   : Named num 3.59

@@

##   .. ..$ T2_threshold    : Named num 61.6

@@

##   .. ..$ projectionMatrix: num [1:6, 1:2] 0.421 -0.389 0.433 0.43 -0.32 ...
##   .. ..$ LambdaInv       : num [1:2, 1:2] 0.202 0 0 1.646
##   .. ..$ muTrain         : Named num [1:6] 1.36 -2.09 2.93 1.35 -2.05 ...

@@

##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 2.58 0 0 0 0 ...

@@

##   .. ..$ SPE_threshold   : Named num 1.35

@@

##   .. ..$ T2_threshold    : Named num 77

@@

##   .. ..$ projectionMatrix: num [1:6, 1:3] 0.5025 -0.0192 -0.4984 0.5267 0.1392 ...
##   .. ..$ LambdaInv       : num [1:3, 1:3] 0.285 0 0 0 0.686 ...
##   .. ..$ muTrain         : Named num [1:6] 2.946 -0.565 -4.465 2.92 -0.59 ...

@@

##   .. ..$ SPE_threshold   : Named num 6.42

@@

##   .. ..$ T2_threshold    : Named num 85.4

@@

##   .. ..$ projectionMatrix: num [1:6, 1:2] -0.399 -0.453 -0.454 0.152 -0.462 ...
##   .. ..$ LambdaInv       : num [1:2, 1:2] 0.275 0 0 0.501
##   .. ..$ muTrain         : Named num [1:6] 0.526 0.268 1.411 0.566 0.254 ...

@@

##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 16.8 0 0 0 0 ...

@@

\subsubsection{Adding Lagged Features}
First, concatenate the last given observation from the training set as ``row 0'' of the test data set. This will enable \texttt{mspMonitor} to include lag-1 features. Similarly, one would include the last $k$ observations of the training set should the process dictate the need for any lag-$k$ features. Because the Fault Start Index was set to 8500, this testing window will show the change point between observations generated under normal conditions and those generated under a fault state.
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{test1A_xts} \hlkwb{<-} \hlstd{fault1A_xts[}\hlnum{8460}\hlopt{:}\hlnum{8520}\hlstd{,} \hlopt{-}\hlnum{1}\hlstd{]}
\hlstd{lagTest1A_xts} \hlkwb{<-} \hlkwd{lag.xts}\hlstd{(test1A_xts,} \hlnum{0}\hlopt{:}\hlnum{1}\hlstd{)}
\hlstd{lagTest1A_xts} \hlkwb{<-} \hlkwd{cbind}\hlstd{(fault1A_xts[}\hlnum{8461}\hlopt{:}\hlnum{8520}\hlstd{,}\hlnum{1}\hlstd{],}
                       \hlstd{lagTest1A_xts[}\hlopt{-}\hlnum{1}\hlstd{,])}
\hlkwd{head}\hlstd{(lagTest1A_xts)}
\end{alltt}
\begin{verbatim}
##                     state         x         y         z       x.1
## 2015-05-22 07:00:00     1 0.4542266 -1.188745 0.6005185 0.3809131
## 2015-05-22 07:01:00     1 0.4889364 -1.416970 0.5952562 0.4542266
## 2015-05-22 07:02:00     1 0.6942253 -1.436590 0.9416095 0.4889364
## 2015-05-22 07:03:00     1 0.5357452 -1.563710 0.9727830 0.6942253
## 2015-05-22 07:04:00     1 0.6569141 -1.504261 0.9597280 0.5357452
## 2015-05-22 07:05:00     1 0.5957465 -1.298968 0.6082284 0.6569141
##                             y.1       z.1
## 2015-05-22 07:00:00  0.09361165 0.3698668
## 2015-05-22 07:01:00 -1.18874504 0.6005185
## 2015-05-22 07:02:00 -1.41696998 0.5952562
## 2015-05-22 07:03:00 -1.43659004 0.9416095
## 2015-05-22 07:04:00 -1.56371006 0.9727830
## 2015-05-22 07:05:00 -1.50426070 0.9597280
\end{verbatim}
\end{kframe}
\end{knitrout}

\subsubsection{Monitoring the Test Data}
With the lagged test observations in the working environment, the \texttt{mspMonitor} function can be applied. This function (similarly to \texttt{mspTrain}) takes in the label information as a separate argument from the input data. Further, the \texttt{mspMonitor} function takes in the \texttt{TrainingSpecs} object returned in the results list from \texttt{mspTrain}. Notice that the first six rows of the monitor matrix are the exact same as the first six rows of the lagged test matrix, except that the rows of the monitor matrix have the monitoring statistic and corresponding indicator columns appended.
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{monitor1A_xts} \hlkwb{<-} \hlkwd{mspMonitor}\hlstd{(}\hlkwc{observations} \hlstd{= lagTest1A_xts[,}\hlopt{-}\hlnum{1}\hlstd{],}
                            \hlkwc{labelVector} \hlstd{= lagTest1A_xts[,}\hlnum{1}\hlstd{],}
                            \hlkwc{trainingSummary} \hlstd{= train1A_ls}\hlopt{$}\hlstd{TrainingSpecs)}
\hlkwd{head}\hlstd{(monitor1A_xts)}
\end{alltt}
\begin{verbatim}
##                             x         y         z       x.1         y.1
## 2015-05-22 07:00:00 0.4542266 -1.188745 0.6005185 0.3809131  0.09361165
## 2015-05-22 07:01:00 0.4889364 -1.416970 0.5952562 0.4542266 -1.18874504
## 2015-05-22 07:02:00 0.6942253 -1.436590 0.9416095 0.4889364 -1.41696998
## 2015-05-22 07:03:00 0.5357452 -1.563710 0.9727830 0.6942253 -1.43659004
## 2015-05-22 07:04:00 0.6569141 -1.504261 0.9597280 0.5357452 -1.56371006
## 2015-05-22 07:05:00 0.5957465 -1.298968 0.6082284 0.6569141 -1.50426070
##                           z.1       SPE SPE_Flag        T2 T2_Flag Alarm
## 2015-05-22 07:00:00 0.3698668 2.0491906        0 25.423541       0    NA
## 2015-05-22 07:01:00 0.6005185 0.1819048        0  6.563964       0    NA
## 2015-05-22 07:02:00 0.5952562 0.3945702        0  5.086740       0    NA
## 2015-05-22 07:03:00 0.9416095 0.1778764        0  4.277330       0    NA
## 2015-05-22 07:04:00 0.9727830 0.1784149        0  4.399492       0    NA
## 2015-05-22 07:05:00 0.9597280 1.1749990        0  5.393532       0    NA
\end{verbatim}
\end{kframe}
\end{knitrout}
